---
title: "A brief guide to using gomfish R package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## 1. Installation

First, load the gomfish package and it's dependencies

```{r setup, results = "hide"}
# Load package
devtools::install_github("Social-Oceans-Lab/gomfish")
library(tidyverse)
```


## 2. Datasets

## 3. Inspecting datasets

Every dataset is documented with metadata. To view the metadata for a dataset, use the `?` command. For example, if you wanted to look at the meta-data for the `cdfw_ports` dataset, you would do the following:

```{r }
# Examine the metadata for the cdfw_port dataset
?cdfw_ports
```

This will pop up a description of the dataset and its columns in the "Help" screen of your R text editor.


## 4. Saving the dataset as an object

You can save the dataset as an object in your R environment using the assingment operator:

```{r }
# Save a dataset in your R environment
data <- wcfish::cdfw_ports
```


## 5. Preparing a quick plot of the dataset

We encourage you to work with the data and plot it based on your own needs. However, we also provide a `plot_data` function for generating a quick plot of the dataset of interest. Note that this only works for the CDFW datasets.

```{r fig.width=7, fig.height=4}
# Quickly plot a CDFW dataset
wcfish::plot_data("cdfw_ports")
```
